
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message =FALSE}
library(plyr)
library(dplyr)
library(readr)
library(tidyverse)
library(modelr)
library(purrr)
library(lubridate)

```

#data input and cleaning

```{r}
setwd("/Users/nikhilg/IDMP")
mydir = "Project"
path1 <- file.path(mydir, "netflix-rotten-tomatoes-metacritic-imdb.csv")
df <- read_csv(path1, show_col_types = FALSE)

```

```{r}
sum(is.na(df))
```

```{r}
cbind(
   lapply(
     lapply(df, is.na)
     , sum)
   )
```

```{r}
head(df)
names(df) <- make.names(names(df), unique=TRUE)
#Create new Score attribute by combining IMDB score and rotten tomatoes score
df <- df %>% 
  mutate(Score = if_else(is.na(IMDb.Score)==FALSE, IMDb.Score, Rotten.Tomatoes.Score/10))
         
print(sum(is.na(df$Score)))
df = df %>% drop_na(Score)
print(sum(is.na(df$Score)))
head(df)


```

```{r}
cbind(
   lapply(
     lapply(df, is.na)
     , sum)
   )
```

```{r}
#Deleting Rotten.Tomatoes.Score and IMDb.Score as it is replaced by Score
df = subset(df, select = -c(Rotten.Tomatoes.Score,IMDb.Score,Metacritic.Score,Awards.Nominated.For, Awards.Received,Production.House,TMDb.Trailer,Trailer.Site))

head(df)

```

```{r}
df = df %>%
  separate_rows(Tags, sep = ",")
df = df %>%
  separate_rows(Director, sep = ",")
df = df %>%
  separate_rows(Genre, sep = ",")
df = df %>%
  separate_rows(Actors, sep = ",")
df = df %>%
  separate_rows(Writer, sep = ",")
df = df %>%
  separate_rows(Country.Availability, sep = ",")
#df= df %>%
 # separate_rows(Languages, sep = ",")

head(df)
```

```{r}
sum(is.na(df))
df <- na.omit(df)
sum(is.na(df))
```

```{r}
cbind(
   lapply(
     lapply(df, is.na)
     , sum)
   )
```

```{r}
length(unique(df[["Director"]]))
length(unique(df[["Writer"]]))


```

```{r}
# Dividing the data set into movies and series.

df_movies = filter(df, Series.or.Movie == "Movie")
df_series = filter(df, Series.or.Movie == "Series")

head(df_movies)
head(df_series)
df_movies = drop_na(df_movies)
df_series = drop_na(df_series)
sum(is.na(df_movies))
sum(is.na(df_series))

```

Taking up a lot of space: these two funtions

df_movies = df_movies %>% separate_rows(Languages, sep = ",") df_series
= df_series %>% separate_rows(Languages, sep = ",") df_movies

df_1 = df_1 %>% arrange(desc(Score)

#Director ## In Movies

```{r}
length(unique(df_movies[["Director"]]))
df_1 = subset(df_movies, select = -c(Poster,Image,IMDb.Votes,	
Summary,IMDb.Link,Netflix.Link,Netflix.Release.Date,Boxoffice,View.Rating,Actors,Writer,Runtime,Country.Availability,Hidden.Gem.Score
,Series.or.Movie,Languages,Tags,Genre,Title))
df_1
df_2 <- df_1 %>%
  group_by(Director) %>%
  summarise_at(vars(Score), list(Score = mean)) %>% arrange(desc(Score))
df_2

df_2=df_2[1:11,]    
df_2
ggplot(df_2,aes(y=Director,x=Score)) +
  geom_point(color='darkblue') +
  theme_minimal()
df_2=df_2[1:6,]
df_2
```

#in series

```{r}
df_series
df_3 = subset(df_series, select = -c(Poster,Image,IMDb.Votes,	
Summary,IMDb.Link,Netflix.Link,Netflix.Release.Date,Boxoffice,View.Rating,Actors,Writer,Runtime,Country.Availability,Hidden.Gem.Score
,Series.or.Movie,Languages,Tags,Genre,Title))
df_3
df_4 <- df_3 %>%
  group_by(Director) %>%
  summarise_at(vars(Score), list(Score = mean)) %>% arrange(desc(Score))
df_4

df_4=df_4[1:11,]
df_4
ggplot(df_4,aes(y=Director,x=Score)) +
  geom_point(color='darkblue') +
  theme_minimal()
df_4=df_4[1:5,]
df_4
```

#Writer ##movies

```{r}

length(unique(df_movies[["Writer"]]))
df_5 = subset(df_movies, select = -c(Poster,Image,IMDb.Votes,	
Summary,IMDb.Link,Netflix.Link,Netflix.Release.Date,Boxoffice,View.Rating,Actors,Director,Runtime,Country.Availability,Hidden.Gem.Score
,Series.or.Movie,Languages,Tags,Genre,Title))
df_5
df_6 <- df_5 %>%
  group_by(Writer) %>%
  summarise_at(vars(Score), list(Score = mean)) %>% arrange(desc(Score))
df_6

df_6=df_6[1:11,]    
df_6
ggplot(df_6,aes(y=Writer,x=Score)) +
  geom_point(color='darkblue') +
  theme_minimal()
df_6=df_6[1:5,]    
df_6
```

##series

```{r}

length(unique(df_series[["Writer"]]))
df_7 = subset(df_series, select = -c(Poster,Image,IMDb.Votes,	
Summary,IMDb.Link,Netflix.Link,Netflix.Release.Date,Boxoffice,View.Rating,Actors,Director,Runtime,Country.Availability,Hidden.Gem.Score
,Series.or.Movie,Languages,Tags,Genre,Title))
df_7
df_8 <- df_7 %>%
  group_by(Writer) %>%
  summarise_at(vars(Score), list(Score = mean)) %>% arrange(desc(Score))
df_8

df_8=df_8[1:11,]    
df_8
ggplot(df_8,aes(y=Writer,x=Score)) +
  geom_point(color='darkblue') +
  theme_minimal()
df_8=df_8[1:5,]    
df_8

```

```{r}

df_1
df_3
df_5
df_7

df_1$Release.Date <- dmy(df_1$Release.Date)
df_3$Release.Date <- dmy(df_3$Release.Date)
df_5$Release.Date <- dmy(df_5$Release.Date)
df_7$Release.Date <- dmy(df_7$Release.Date)


df_1
df_3
df_5
df_7
df_2

```

```{r}

sum(is.na(df_movies))
df_movies
df_8 <- df_movies %>%
  group_by(Director) %>%
arrange(desc(Release.Date))
df_8
df_8 = subset(df_8, select = -c(Poster,Image,IMDb.Votes,	
Summary,IMDb.Link,Netflix.Link,Netflix.Release.Date,Boxoffice,View.Rating,Actors,Writer,Runtime,Country.Availability,Hidden.Gem.Score
,Series.or.Movie,Languages,Tags,Genre,Title))
df_8
df
```

ignore this part have to amek few changes here

```{r}
length(unique(df[["Runtime"]]))
unique(df[["Runtime"]])
by_runtime <- group_by(df, Runtime)
by_runtime
#summarise(data, mean_score = mean(Score, na.rm = TRUE))

df_rt <- df %>%
  group_by(Runtime) %>%
  summarise_at(vars(Score), list(Score = mean)) %>% arrange(desc(Runtime))
df_rt
df_rt <- df_rt[1:4,]
df_rt
ggplot(df_rt,aes(y=Score,x=Runtime)) +
  geom_point(color='darkblue') +
  theme_minimal()
```

Director Ratings over the decades (Vishnu) Writer Ratings over the
decades (Vishnu)

# PCA

```{r}
library(tidyverse)
df_class = df
df_class = drop_na(df_class)
summary(df_class)
head(df_class)
as_tibble(df_class)
```

```{r}
df_Class <- df_class[,c(6,22)]

head(df_Class)
df_Class <- as.matrix(df_Class)
df_genre <- df_class$Genre
table(df_genre)
```

```{r}

df_new = subset(df_series, select = -c((1:5)))
df_new = subset(df_new, select = -c((2:13)))
df_new = subset(df_new, select = -c((3:4)))
df_new1 = subset(df_new, select = -c((2:3)))
head(df_new)
df_movie_n <- sample_n(df_movies, 60000)
df_movie_n
df_new2 = subset(df_movie_n, select = -c((1:5)))
df_new3 = subset(df_new2, select = -c((2:17)))

```

```{r}
library(dendextend)
dist_mat <- dist(df_Class, method = 'euclidean')
hc1 <- hclust(dist_mat, method="complete")
plot(hc1)
avg_dend_obj <- as.dendrogram(hc1)
avg_col_dend <- color_branches(avg_dend_obj, h = 7.3)
plot(avg_col_dend)
```

```{r}
library(Rtsne)
library(tidyverse)
df_new2 = subset(df_class, select = -c((1:5)))
df_new3 = subset(df_new2, select = -c((2:19)))
set.seed(1)
tsne2 <- Rtsne(df_new3, perplexity=10, check_duplicates = FALSE)

colnames(tsne2$Y) <- c("C1", "C2")

tc2 <- as_tibble(tsne2$Y)
tc2
```

```{r}
hc1_cl <- factor(cutree(hc1, k=4))
ggplot(df_class, aes(x=Score, y=Hidden.Gem.Score, color=hc1_cl, shape=hc1_cl)) +
  geom_point() +
  scale_color_brewer(palette="Set1") +
  labs(shape="Cluster" ,color="Cluster",
       title="Complete linkage") +
  theme_minimal()
```

```{r}
hc2 <- hclust(dist(df_Class), method="average")
plot(hc2)
avg_dend_obj <- as.dendrogram(hc2)
avg_col_dend <- color_branches(avg_dend_obj, h = 3)
plot(avg_col_dend)
```

```{r}
hc2_cl <- factor(cutree(hc2, k=4))
ggplot(df_class, aes(x=Score, y=Hidden.Gem.Score, color=hc2_cl, shape=hc2_cl)) +
  geom_point() +
  scale_color_brewer(palette="Set1") +
  labs(shape="Cluster", color="Cluster",
       title="Average linkage") +
  theme_minimal()
```

```{r}
set.seed(1)
km <- kmeans(df_new3, centers=3)
```

```{r}
km_cl <- factor(km$cluster)
ggplot(df_class, aes(x=Score, y=Hidden.Gem.Score, color=km_cl, shape=km_cl)) +
  geom_point() +
  scale_color_brewer(palette="Set1") +
  labs(shape="Cluster", color="Cluster") +
  theme_minimal()
```
